\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{PHYS263 Lab 3}
\author{Hazel Brown\\[1ex]
\small{Partner: Muz Shah}}
\date{September 27, 2024}

\begin{document}

\maketitle

\section{Introduction}



\section{Questions}

\subsection{Reflection}

\begin{itemize}
    \item What relationship holds between the angle of incidence and the angle of reflection? Does this relationship hold for all angles of incidence?

    \item In measuring the angle of reflection, you measured the angle at which a maximum meter reading was found. Can you explain why some of the wave reflected into different angles? How does this affect your answer to question 1?

    \item Ideally you would perform this experiment with a perfect plane wave, so that all the Transmitter radiation strikes the Reflector at the same angle of incidence. Is the microwave from the Transmitter a perfect plane wave (Consider how you could test this)? Would you expect different results if it were a perfect plane wave? Explain.


    
\end{itemize}

\subsection{Refraction through a prism}
3
Would you expect the refraction index of the styrene pellets in the prism mold to be the same as for a solid styrene prism?

\subsection{Polarization}

\begin{itemize}

\item Based on your data from rotating the polarizer when starting with the horns aligned, how does the Polarizer affect the incident microwave?

\item Can you explain the results of the last step of the polarization experiment? 

\item How can the insertion of an additional polarizer increase the signal level at the detector?

\end{itemize}

\end{document}
